Individual Specific Allele Frequency

### 2019-02-28 rick/1kGP_lukeMod.Rmd
modified ricks code a bit

```{r}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file(), fig.width=16)
options(scipen=999)
```
```{bash}
wget https://raw.githubusercontent.com/bwlewis/1000_genomes_examples/master/parse.c
cc -O2 parse.c
```

```{r}
library(Matrix)
library(irlba)
library(threejs)
library(tidyverse)
library(lfa)

library(glm2)
```

@@

Logistic Regression
```{r}
LF = mapply(function(x, y){
                           glm(x 
                                ~ bas_dt$avg_qual 
                                + offset(y))}, 
                           as.data.frame(t(chr22_mtx)),
                           as.data.frame(t(subset)))

@@

>>>>

#```{r}
#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file(), fig.width=16)
#options(scipen=999)
#```
```{bash}
wget https://raw.githubusercontent.com/bwlewis/1000_genomes_examples/master/parse.c
cc -O2 parse.c
```

```{r}
library(Matrix)
library(irlba)
library(threejs)
library(tidyverse)
library(lfa)
library(furrr)plots
library(glm2)
```

@@

```{r}
chr22sub_ial <- af(chr22_mtx, LF)

@@

to_datalist <- function(i, data_genotype, data_iaf, qual){

    data <- tibble(genotype=data_genotype[i,],
               iaf=data_iaf[i,],
               qual=qual)

     return(data)       
}

fit_model_1 <- function(data){

  fit <- glm2(genotype ~ qual + offset(iaf), family ="binomial", data=data)
  return(fit)

}

plot_data <- function(data){

      p <- ggplot(data,
       aes(qual, genotype, color=iaf)) +
      geom_point() +
      theme_bw()
  return(p)

}
```

loci <- seq(1,50000)
names(loci) <- loci

data_list <- map(loci, 
                 to_datalist,
                 data_genotype=chr22_mtx,
                 data_iaf=chr22sub_ial,
                 qual=bas_dt$avg_qual)

```{r}
options(future.globals.maxSize= 6000000000)

fits <- future_map(data_list, fit_model_1)

```{r}
coefLF = lapply(fits, function(x) coef(x)[[2]])

```{r}
plots <-  future_map(data_list, plot_data) 
```
